Batch, Off-policy and Model-free Apprenticeship Learning

### 2013-07-25 Manuscrit/titlepage.tex
Typo title page

\vspace{0.5cm}
% \hfill
\vfill

\noindent \textbf{Membres du jury}\noindent\\ \noindent
\begin{tabularx}{18cm}{p{2.6cm}p{3.6cm}p{10.5cm}}
Examinateurs & Yann Guermeur &\small{Equipe ABC, Loria-CNRS -- Nancy (directeur de thèse)}\\
 &Matthieu Geist &\small{Equipe IMS-MaLIS, Supélec -- Metz (codirecteur de thèse)}\\
 &Olivier Pietquin &\small{Equipe IMS-MaLIS, Supélec -- Metz}\\
 &Manuel Lopes&\small{Equipe Flowers, INRIA -- Bordeaux}\\
 Raporteurs&Rachid Alami &\small{LAAS /  CNRS -- Toulouse}\\
 &Brahim  Chaib-draa&\small{DAMAS, Université Laval -- Québec} 
\end{tabularx}

\vspace{5em}

>>>>

%\vspace{0.5cm}

\noindent \textbf{Membres du jury}\noindent\\ \noindent
\begin{tabularx}{18cm}{p{3cm}p{4cm}p{10.5cm}}
Directeurs de thèse & Yann Guermeur &\small{Equipe ABC, Loria-CNRS -- Nancy}\\
 &Matthieu Geist &\small{Equipe IMS-MaLIS, Supélec -- Metz}\\
 Rapporteurs&Rachid Alami &\small{LAAS /  CNRS -- Toulouse}\\
 &Brahim  Chaib-draa&\small{DAMAS, Université Laval -- Québec}\\ 
Examinateurs &Sylvain Contassot-Vivier&\small{Loria-Université de Lorraine -- Nancy}\\
 &Manuel Lopes&\small{Equipe Flowers, INRIA -- Bordeaux}\\
&Guillaume Laurent&\small{Institut FEMTO-ST / ENSMM, Besançon}\\
&Olivier Pietquin &\small{Equipe IMS-MaLIS, Supélec -- Metz}
\end{tabularx}

\vspace{4em}
